%-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom cokmands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Diego Llanes -- Machine Learning Research Assistant} % Your Name
\newcommand{\course}{Computer Science} % Your Program
%\newcommand{\roll}{W01574143} % Your Roll No.
\newcommand{\phone}{720-431-8494} % Your Phone Number
\newcommand{\emaila}{research@diegollanes.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\LARGE \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ \href{tel:17204318494}{+1 \phone}}\\
  Western Washington University Computer Science Pre-Masters & \href{https://github.com/Diego-Llanes}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}} \\  
  {} & \href{https://www.linkedin.com/in/diego-llanes-ai/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}} \\
  {} & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
\end{tabularx}
}

\vspace{-9.0mm}

%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      { Bachelor of Science in Computer Science}{GPA: 3.5}
      {Western Washington University Computer Science}{January 2021 - June 2024 (Expected)}
      
    \resumeSubheading
      { Master of Science in Computer Science}{GPA: 4.0}
      {Western Washington University Computer Science}{September 2023 - June 2025 (Expected)}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}
%

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      { Scientific Machine Learning Technical Intern}{Remote, Richland WA}
      {Pacific Northwest National Laboratories (PNNL)}{July 2022 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
    % \item {Trained a RNN based architecture to simulate a building and its HVAC system by mapping current state spaces, disturbances, and controls, to subsequent state spaces.}
    % \item {Trained a DPC agent (Drgoňa, 2022) to control the RNN based building simulation to minimize energy usage and ensure thermal comfort.} 
    \item {Benchmarked the use of Differentiable Predictive Control (Drgoňa, 2022) against traditional model-free Deep Reinforcement Learning algorithms and contributed to an open source project.}
    \item {Worked with domain experts in Energy Efficient Building Control to understand how to best model the real world physics of these systems.}
    \item {Gained in-depth understanding of Control Theory, Reinforcement Learning, and their applications.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
    
    \resumeSubheading
      { Deep Learning Research Assistant}{Bellingham WA}
      {Hutchinson Machine Learning Research Group}{September 2022 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Trained and tuned computer vision inspired CNN-based architectures (BOSS Net, PHOENIX Net, HYDRA Net) to extract features from spectroscopy data to predict a stellar object's surface gravity, temperature, and metallicity.}
    \item {Read and discussed state-of-the-art research papers weekly to learn about novel  machine/deep learning techniques.}
    \item {Gained a strong knowledge of libraries like PyTorch, Matplotlib, NumPy, and Pandas.}
    \item {Built various "Slack Bots" using the SlackSDK API, to increase productivity and workspace morale.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}

    \resumeSubheading
      { Graduate Course Teaching Assistant}{Bellingham WA}
      {Western Washington University}{March 2023 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Developed visualization tools to help students better understand machine learning concepts.}
    \item {Created worksheets to help students more critically engage with the content that they learned in class.}
    \item {Built curriculum and lectured on course material to illuminate challenging concepts.}
    \item {Worked with students one-on-one to meet their learning targets and to address their misunderstandings.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  
\vspace{-8.5mm}

%-------------------------------------------
\section{\textbf{Publications}}
% \vspace{-0.4mm}
\begin{itemize}[leftmargin=*]
     \setlength\itemsep{-0.25em}
     \item {Sizemore, L., \textbf{Llanes, D.}, Kounkel, M., Hutchinson, B., Stassun, K. G., \& Chandra, V. A self-consistent data-driven model for determining stellar parameters from optical and near-IR spectra. Astronomical Journal (accepted).
     \href{https://arxiv.org/abs/2402.05184}{https://arxiv.org/abs/2402.05184}}
     \item {Briney, S., \textbf{Llanes, D.}, Qiang, H., Shapiro, M., Drgona, J., Tuor, \& A., Hutchinson, B. Comparing Deep Reinforcement Learning and Differentiable Predictive Control for Building Emulator Control Policy Optimization. Abstract accepted, manuscript in preparation.}
\end{itemize}

\vspace{-5.5mm}
%-----------Achievements-----------------
\section{\textbf{Scholarly Presentations}}
% \vspace{-0.4mm}
\resumeSubHeadingListStart
     \setlength\itemsep{0.05em}

% \resumePOR{ BOSS Net Paper } % Award
%     {-- Published on Arxiv} % Event
%     {February 2024} %Event Year
%     Submitted a paper described ou
    
\resumePOR{ Sloan Digital Sky Survey V Collaboration } % Award
    {-- Research Talk Presenter} % Event
    {July 2023} %Event Year
    Presented contributions to BOSS Net to an audience of astronomers.
\resumePOR{ Western Washington University Scholars Week } % Award
    {-- Poster Presenter} % Event
    {March 2023} %Event Year
    Presented BOSS Net, PHOENIX Net, TRONN contributions to an audience of students and professors.
\resumeSubHeadingListEnd
\vspace{-6mm}


%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart

    \resumeProject
      { Neural Network From Scratch} %Project Name
      { Deep learning Python package written with only NumPy to allow users to build arbitrarily deep neural networks.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Implemented forward and backward propagation, activation functions, and gradient descent for both classification and regression tasks.}
    \resumeItemListEnd
    \vspace{-2mm}
    
    % \resumeProject
    %   { Apple Music CLI} %Project Name
    %   {A command line interface for controlling Apple Music allowing you to pause, play, skip, and "love" songs,} %Project Name, Location Name
    %   {} %Event Dates

    %   \resumeItemListStart
    %     \item {Allows users to interface with their media player without having to leave their productivity behind.}
    %     \item {Technology Used: Go, BubleTea, Apple Script.}
    % \resumeItemListEnd
    % \vspace{-2mm}
    
    % \resumeProject
    %   { Whatcom Community Food Services App} %Project Name
    %   {Created an Android app using Kotlin to help unhoused people find access to shelters, food banks, and food drives.} %Project Name, Location Name
    %   {} %Event Dates

    %   \resumeItemListStart
    %     \item {Used Kotlin and Android studio to develop an Android application to help users gain access to resources that they have known they had access to prior.}
    %    \item {Technology Used: Android Studio, Kotlin, NodeJS.}
    % \resumeItemListEnd
    
    \vspace{-2mm}
  \resumeSubHeadingListEnd
\vspace{-8.5mm}



\quad
%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, Go, BASH, Kotlin, Javascript} \\
     \textbf{Libraries}{: PyTorch, NumPy, Pandas, Matplotlib, SciKit-Learn, Scipy, Tensorflow}\\ 
     \textbf{Frameworks}{: NodeJS, ReactJS} \\
     \textbf{Databases}{: H5py, MySQL } \\  
     \textbf{Documentation}{: LaTeX, Github Markdown, PowerPoint}\\
     \textbf{Relevent Coursework}{: Deep Learning, Machine Learning, Calculus I-III, Linear Algebra I-II, Data Structures \& Algorithms, Object Oriented Programming, Database Management Systems. } \\ 
     \textbf{Areas of Interest}{: Reinforcement Learning, NLP, Control Theory, Differentiable Programming} \\
     \textbf{Soft Skills}{: Problem Solving, Collaborating, Presenting, Communication, Sociability} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------Positions of Responsibility-----------------
% \section{\textbf{Positions of Responsibility}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{ Manager } % Position
%     {Snarf's Sandwiches} %Club,Event
%     {March - Sep 2022} %Tenure Period \\
%     \resumeItemListStart
%     \item {Managed and delegated tasks to a team of 15 to ensure customer satisfaction.}
%     \item {Managed and aided with inventory to ensure supply never dropped under a threshold.}
%     \resumeItemListEnd

% \resumeSubHeadingListEnd
% \vspace{-5mm}

% \resumeSubHeadingListStart
% \resumePOR{ BOSS Net Paper } % Award
%     {-- Published on Arxiv} % Event
%     {February 2024} %Event Year
%     Submitted a paper described ou
    % \resumePOR{} % Award
%     {-- arXiv} % Event
%     {July 2023} %Event Year
%     Presented my contributions to BOSS Net to an audience of astronomers.
% \vspace{-5mm}

% \resumeSubHeadingListEnd

\end{document}
